A Decision Procedure for (Co)datatypes in SMT Solvers

### 2014-12-01 tex/codatadp.tex
sketched an abstract

@@

\begin{abstract}
Blah.
\end{abstract}

@@

  * useful both for proving and for model finding
    * in particular, acyclicity and bisimilarity are necessary for some proofs
      (and cannot be axiomatized finitely)
    * and for model finding, without them we quickly get spurious models

>>>>

\hyphenation{data-type data-types co-data-type co-data-types}

@@

\begin{abstract}
Codatatypes naturally capture potentially infinite data structures and
processes. We introduce a decision procedure that combines reasoning about
datatypes and codatatypes. The dual of the acyclicity rule of datatypes is a
bisimilarity rule that identifies observationally equal values. The procedure is
compatible with the Nelson--Oppen combination method and is useful for both
proving and model finding. It has been implemented in the latest version of
CVC4, a modern SMT solver. An evaluation based on problems generated from
Isabelle/HOL theories demonstrates the potential of the procedure in a proving
context.
\end{abstract}

@@

  * useful both for proving and for model finding
    * in particular, acyclicity and bisimilarity are necessary for some proofs
      (and cannot be axiomatized finitely)
    * and for model finding, without them we quickly get spurious models
    * explain how finite model finding works
